---
title: "Analysis for quantifying electricity supply security in South Korea"
author: "Kenneth Piech"
date: "10/4/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
This is an R markdown document recording analysis for *Quantifying electricity 
supply security in South Korea: historical values and projections* by Kenneth 
Piech.

In section 1 we will load packages and data to prepare for analysis. In section 
2 we format data and perform calculations to prepare for analysis. In section 3
we calculate and visualize values of ESMC, and we calculate
and visualize values of ESPI in section 4. In section 5 we create a table 
documenting the results of our ESMC calculations for each fuel type, and in 
section 6 we produce a visualization of electricity generation by fuel type for
South Korea. 

# 1. Prepare for analysis


### 1.1 Load packages


```{r install_and_load_packages}

# install packages

# install.packages("dplyr")
# install.packages("here")
# install.packages("hrbrthemes")
# install.packages("janitor")
# install.packages("skimr")
# install.packages("tidyverse")
# install.packages("viridis")
# install.packages("webshot")

#load packages

library(dplyr)
library(ggplot2)
library(gt)
library(hrbrthemes)
library(janitor)
library(readr)
library(tidyr)
library(tidyverse)
library(viridis)
library(webshot)
```

```{r set_times_new_roman}

#use Times New Roman font for visualizations

windowsFonts(A = windowsFont("Times New Roman"))

hrbrthemes::import_roboto_condensed()

library(webshot)

webshot::install_phantomjs(force = TRUE)
```


### 1.2 Import data


All world bank and EIA data sets were cleaned and placed in standardized format 
for merging and calculations. 

```{r import_world_bank_world_governance_indices_data}

political_stability <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/political_stability.csv")
  View(political_stability)

regulatory_quality <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/regulatory_quality.csv")
  View(regulatory_quality)

rule_of_law <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/rule_of_law.csv")
  View(rule_of_law)
```

```{r import_EIA_global_oil_exports_data}

eia_country_oil_exports <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/eia_country_oil_exports.csv")
  View(eia_country_oil_exports)
```


# 2. Format data for analysis


```{r merge_three_world_bank_index_dataframes}

#Merge political stability, regulatory quality, and rule of law data frames and
#adjust to create a political risk composite value.

political_join <- full_join(
  political_stability,
  regulatory_quality,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

political_join_2 <- full_join(
  political_join,
  rule_of_law,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

political_composite <- political_join_2 %>% 
  rowwise() %>% 
    mutate(
      risk_composite = mean(c(political_stability, regulatory_quality, 
      rule_of_law))
    )

#risk_composite is an average of the three governance indices. 
```

```{r create_political_risk_multiplier}

#We will use political_risk_multiplier to calculate ESMC and ESPI values in 
#sections 3 and 4. political_risk_multiplier ranges from 1 to 3. 
#HHI values typically range from 0 to 10,000, and our values for ESMC will range 
#from 0 to 30,000 due to the political_risk_multiplier.

political_risk_multiplier <-  mutate(
  political_composite, risk_multiplier = (
  (5 - (risk_composite + 2.5))*
  (2/5) + 1
  )
)
```

```{r merge_oil_export_and_political_risk_dataframes}

oil_risk <- inner_join(
  political_risk_multiplier,
  eia_country_oil_exports,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)
```


# 3. Calculate and visualize ESMC for coal, oil, and gas


### 3.1 Calculate ESMC_oil


```{r calculate_ESMC_oil}
oil_risk_market_share_squared <- mutate(
  oil_risk, "market_share_squared" = 
  (country_oil_exports_mb_per_day * 100 / global_oil_exports_mb_per_day)^2
)

oil_risk_RWMS <- mutate(
  oil_risk_market_share_squared, "RWMS" = market_share_squared * risk_multiplier
)

oil_risk_RWMS_no_na <- na.omit(oil_risk_RWMS)

global_oil_ESMC <- oil_risk_RWMS_no_na %>%
  group_by(year) %>%
  summarise(ESMC = sum(RWMS))
```


### 3.2 Calculate ESMC_coal


We use "thermal coal" export data as reported by the EIA, which 
correspondes to the anthracite, bituminous, and sub-bituminous coals used for 
electricity in South Korea. 

```{r calculate_ESMC_coal}

eia_country_coal_exports <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/eia_country_coal_exports.csv")
  View(eia_country_coal_exports)

coal_risk <- inner_join(
  political_risk_multiplier,
  eia_country_coal_exports,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

coal_risk_market_share_squared <- mutate(
  coal_risk, "market_share_squared" = (
    ( 
      (as.numeric(country_thermal_coal_exports_per_year)) * 100 / 
      (as.numeric(world_thermal_coal_exports_per_year)
       )
    )^2
  )
)

coal_risk_RWMS <- mutate(
  coal_risk_market_share_squared, "RWMS" = market_share_squared * 
  risk_multiplier
)

coal_risk_RWMS_no_na <- na.omit(coal_risk_RWMS)

global_coal_ESMC <- coal_risk_RWMS_no_na %>%
  group_by(year) %>%
  summarise(ESMC = sum(RWMS))
```


### 3.3 Calculate ESMC_gas


```{r calculate_ESMC_gas}

eia_country_gas_exports <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/eia_country_gas_exports.csv")
  View(eia_country_gas_exports)

gas_risk <- inner_join(
  political_risk_multiplier,
  eia_country_gas_exports,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

gas_risk_market_share_squared <- mutate(
  gas_risk, "market_share_squared" = (
    ( (as.numeric(country_gas_exports)) * 100 / (as.numeric(world_gas_exports))
    )^2
  )
)

gas_risk_RWMS <- mutate(
  gas_risk_market_share_squared, "RWMS" = market_share_squared * 
  risk_multiplier
)

gas_risk_RWMS_no_na <- na.omit(gas_risk_RWMS)

global_gas_ESMC <- gas_risk_RWMS_no_na %>%
  group_by(year) %>%
  summarise(ESMC = sum(RWMS))

global_gas_ESMC_1 <- rename(global_gas_ESMC, ESMC_gas = ESMC)

global_oil_ESMC_1 <- rename(global_oil_ESMC, ESMC_oil = ESMC)

global_gas_ESMC_2 <- full_join(
  global_gas_ESMC_1,
  global_oil_ESMC_1,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

#import spot-market proportion GIIGNL data

gas_spot_market_proportions <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/gas_spot_market_proportions.csv")
  View(gas_spot_market_proportions)

global_gas_ESMC_3 <- 
  full_join(
  global_gas_ESMC_2,
  gas_spot_market_proportions,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

global_gas_ESMC_4 <- na.omit(global_gas_ESMC_3)

#create weighted value for ESMC considering proportion of global spot-market vs. oil-indexed sales

global_gas_ESMC_weighted <- mutate(
  global_gas_ESMC_4, 
  "ESMC" = (as.numeric(ESMC_gas))*gas_spot_market_proportion + 
  (as.numeric(ESMC_oil))*gas_oil_indexed_proportion
)
```


### 3.4 Create a comprehensive ESMC dataframe


```{r create_comprehensive_ESMC_dataframe}

global_coal_ESMC_1 = rename(global_coal_ESMC, "ESMC_coal" = "ESMC")

#create global gas ESMC weighed value to join with ESMC_coal

global_gas_ESMC_weighted_1 <- global_gas_ESMC_weighted[c(1,6)]

global_gas_ESMC_weighted_2 <- rename(
  global_gas_ESMC_weighted_1, ESMC_gas = ESMC
)

# join ESMC gas and oil to prepare to join to ESMC coal

global_gas_ESMC_weighted_3 <- full_join(
  global_gas_ESMC_weighted_2,
  global_oil_ESMC_1,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

#join all ESMC values to make a comprehensive dataframe 

global_ESMC_comprehensive <- full_join(
  global_gas_ESMC_weighted_3, global_coal_ESMC_1
)
```


### 3.5 Add projections for 2022, 2030, and 2034 to historical dataframes 


We will assume ESMC for coal, gas, and oil each remain at the average of their
levels from 2014-2018 through 2022, 2030, and 2034. 

```{r import_assumed_future_ESMC_values_based_on_2014-2018_average_values}

X2014_to_2018_avg_ESMC_coal <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/2014_to_2018_avg_ESMC_coal.csv")

X2014_to_2018_avg_ESMC_gas <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/2014_to_2018_avg_ESMC_gas.csv")

X2014_to_2018_avg_ESMC_oil <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/2014_to_2018_avg_ESMC_oil.csv")

#merge projected data with historical data for ESMC

global_gas_ESMC_projected_0 <- full_join(
  global_gas_ESMC_weighted,
  X2014_to_2018_avg_ESMC_gas,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never")
)

global_gas_ESMC_projected <- global_gas_ESMC_projected_0[c(1:23),c(1,6)]

global_oil_ESMC_projected <- full_join(
  global_oil_ESMC,
  X2014_to_2018_avg_ESMC_oil,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never"))

global_coal_ESMC_projected <- full_join(
  global_coal_ESMC,
  X2014_to_2018_avg_ESMC_coal,
  by = NULL,
  copy = FALSE,
  suffix = c(".x", ".y"),
  keep = FALSE,
  na_matches = c("na", "never"))

#rename ESMC for more specific ESMC values and merge dataframes for oil, coal, 
#and gas

global_coal_ESMC_projected_1 = rename(
  global_coal_ESMC_projected, "ESMC_coal" = "ESMC"
)

global_gas_ESMC_projected_1 = rename(
  global_gas_ESMC_projected, "ESMC_gas" = "ESMC"
)

global_oil_ESMC_projected_1 = rename(
  global_oil_ESMC_projected, "ESMC_oil" = "ESMC"
)

#merge the three dataframes to create one dataframe with all historical and 
#projected ESMC values

global_ESMC_coal_and_gas_projected <- full_join(
  global_coal_ESMC_projected_1, global_gas_ESMC_projected_1
)

global_ESMC_comprehensive_projected <- full_join(
  global_ESMC_coal_and_gas_projected, global_oil_ESMC_projected_1
)
```


### 3.6 Plot historical ESMC values


```{r change_ESMC_data_to_long_format_and_merge_to_plot}

global_coal_ESMC_long <- global_coal_ESMC %>%
  add_column(Fuel = "coal")

global_gas_ESMC_long <- global_gas_ESMC_weighted %>%
  add_column(Fuel = "gas")

#select only required variables to vertically merge gas data with coal and oil data

global_gas_ESMC_long_1 <- global_gas_ESMC_long[c(1,6:7)]

global_oil_ESMC_long <- global_oil_ESMC %>%
  add_column(Fuel = "oil")

#vertically merge coal, gas, and oil ESMC values to plot together

global_ESMC_comprehensive_long <- rbind(
  global_coal_ESMC_long, global_gas_ESMC_long_1, global_oil_ESMC_long
)

#plot all ESMC values together using comprehensive long data

global_ESMC_comprehensive_long %>%
  ggplot(mapping = aes(x=year, y=ESMC, color=Fuel)) + 
  ylab(expression(paste("ESM",C[pol-f]))) + 
  xlab(expression(paste("Year"))) +
  geom_line(method='lm', se=FALSE) +
  geom_point(aes(shape=Fuel)) +
  theme_minimal() + 
  scale_colour_viridis(discrete = T, option = "H") +
  expand_limits(y=0) + geom_point() +
  labs(title=(expression(paste("Historical ESM", C[pol-f], " by fuel"))
              ), subtitle = "global, 1996-2018"
       ) +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = 
        element_text(hjust = 0.5)) +
  theme(legend.title = element_blank()) +
    theme(text = element_text(family = "A"))
```


### 3.7 Plot area chart of ESMC_coal contributions by country

Code in following chunk adapted from Charles Bordet as cited by Matt Mazur (2017):
[mattmazur.com](https://mattmazur.com/2017/04/19/removing-gaps-from-stacked-area-charts-in-r/)
We use the tidyr 'spread' and 'gather' functions to create a continuous area 
chart by replacing null values with zero values. 


```{r plot_ESMC_coal_area_chart}

#filter out contributions less than or equal to10 units to enhance readability 
#and plot area chart of ESMC_coal 

coal_risk_RWMS_no_na_greater_than_10 <- filter(coal_risk_RWMS_no_na, RWMS > 10)

coal_risk_RWMS_no_na_greater_than_10_cleaned <- 
  coal_risk_RWMS_no_na_greater_than_10[c(2,3,16)]

coal_RWMS_area <- coal_risk_RWMS_no_na_greater_than_10_cleaned %>%
    tidyr::spread(key = wb_country, value = RWMS, fill = 0)
  
coal_RWMS_area_1 <- coal_RWMS_area %>% 
  tidyr::gather(key = wb_country, value = RWMS, -year)

#plot area chart of ESMC_coal contributions by country 

coal_RWMS_area_1 %>% ggplot(mapping=aes(x=year,y=RWMS,fill=wb_country)) + 
  geom_area(alpha=0.65 , size=0.1, colour="black") +
  scale_fill_viridis(discrete = T, option = "H", 
                       
#remove underscores from key labels and replace them with spaces by coercing
#lables: 
                       
  labels = c("Australia","China","Colombia","Indonesia","Kazakhstan",
             "North Korea","Netherlands","Poland","Russia","South Africa",
             "United States","Vietnam")) +
  
#label coercion complete
  
  theme_minimal() +
  labs(title=(expression(paste("Historical ESM", C[pol-coal], 
                               " contributions by country"))), subtitle = 
    "global, 1996-2018", 
    caption = expression(paste(
  "Only contributions greater than 20 displayed to enhance readability"))) +
  ylab(expression(paste("ESM",C[pol-coal], " contribution"))) + 
  xlab(expression(paste("Year"))) +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = 
        element_text(hjust = 0.5)) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(family = "A"))
```


### 3.8 Plot area chart of ESMC_gas contributions by country

Code in following chunk adapted from Charles Bordet as cited by Matt Mazur (2017):
[mattmazur.com](https://mattmazur.com/2017/04/19/removing-gaps-from-stacked-area-charts-in-r/)


```{r plot_ESMC_gas_area_chart}

#filter out contributions less than or equal to 20 units to enhance readability
#and plot area chart of ESMC_gas contributions by country

gas_risk_RWMS_no_na_greater_than_20 <- filter(gas_risk_RWMS_no_na, RWMS > 20)

#adjust data format to produce a smooth area chart

gas_risk_RWMS_no_na_greater_than_20_cleaned <- 
  gas_risk_RWMS_no_na_greater_than_20[c(2,3,13)]

gas_RWMS_area <- gas_risk_RWMS_no_na_greater_than_20_cleaned %>%
  tidyr::spread(key = wb_country, value = RWMS, fill = 0)
  
gas_RWMS_area_1 <- gas_RWMS_area %>% 
  tidyr::gather(key = wb_country, value = RWMS, -year)
  
#plot area chart of ESMC_gas contributions by country

gas_RWMS_area_1 %>% ggplot(mapping=aes(x=year,y=RWMS,fill=wb_country)) + 
     geom_area(alpha=0.65 , size=0.1, colour="black") +
    scale_fill_viridis(discrete = T, option = "H",
                       
##replace underscores with spaces in key labels by coercion
                       
  labels = c("Algeria","Australia","Canada","Indonesia",
             "Malaysia","Netherlands","Norway","Qatar",
            "Russia","Turkmenistan","United States")
  
##label coercion complete
                    
                       ) +
    theme_minimal() +
  labs(title=(expression(paste("Historical spot-market ESM", C[pol-gas], 
      " contributions by country"))), subtitle = "global, 1996-2018", caption =
      "Only contributions greater than 20 displayed to enhance readability") +
  ylab(expression(paste("ESM",C[pol-gas], " contribution"))) + 
  xlab(expression(paste("Year"))) +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = 
        element_text(hjust = 0.5)) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(family = "A"))
```


### 3.9 Plot area chart of ESMC_oil contributions by country

Code in following chunk adapted from Charles Bordet as cited by Matt Mazur (2017):
[mattmazur.com](https://mattmazur.com/2017/04/19/removing-gaps-from-stacked-area-charts-in-r/)


```{r plot_ESMC_oil_area_chart}

#Filter out contributions less than or equal to 20 units to enhance readability

oil_risk_RWMS_no_na_greater_than_20 <- filter(oil_risk_RWMS_no_na, RWMS > 20)

#create a dataframe that will produce a smooth area chart 

oil_risk_RWMS_no_na_greater_than_20_cleaned <- 
  oil_risk_RWMS_no_na_greater_than_20[c(2,3,13)]

oil_RWMS_area <- oil_risk_RWMS_no_na_greater_than_20_cleaned %>%
  tidyr::spread(key = wb_country, value = RWMS, fill = 0)
  
oil_RWMS_area_1 <- oil_RWMS_area %>% 
  tidyr::gather(key = wb_country, value = RWMS, -year)

#plot area chart of ESMC_gas contribution by country

oil_RWMS_area_1 %>% ggplot(mapping=aes(x=year,y=RWMS,fill=wb_country)) + 
     geom_area(alpha=0.65 , size=0.1, colour="black") +
    scale_fill_viridis(discrete = T, option = "H",
                       
##replace underscores in key labels with spaces by coercion
                       
  labels = c("Angola", "Canada", "Iran", "Iraq", "Kazakhstan", "Kuwait", 
             "Libya", "Mexico", "Nigeria", "Norway", "Russia", "Saudi Arabia", 
             "United Arab Emirates", "United Kingdom", "United States", 
             "Venezuela")
  
##label coercion complete
        
                       ) +
    theme_minimal() +
  labs(title=(expression(paste("Historical ESM", C[pol-oil], " contributions by country"))), subtitle = "global, 1996-2018", caption =
      "Only contributions greater than 20 displayed to enhance readability") +
  expand_limits(y=1600) +
  ylab(expression(paste("ESM",C[pol-oil], " contribution"))) + 
  xlab(expression(paste("Year"))) +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = 
        element_text(hjust = 0.5)) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(family = "A"))
```


# 4. Calculate and plot historical and projected ESPI_gen values


```{r calculate ESPI_gen}
#import historical Korea electricity generation data

korea_electricity_generation <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/korea_electricity_generation.csv")

ESMC_and_generation <- inner_join(
  global_ESMC_comprehensive, korea_electricity_generation
)

ESPI_gen <- mutate(
  ESMC_and_generation, "ESPI_gen" = coal_electricity_percent*ESMC_coal/100 + 
  oil_electricity_percent*ESMC_oil/100 + gas_electricity_percent*ESMC_gas/100 + 
  nuclear_and_renewables_electricity_percent*0/100
)

#import planned Korea electricity generation data from BPLE and join projected 
#ESMC data with projected generation data

korea_electricity_generation_projected <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/korea_electricity_generation_projected.csv")

korea_electricity_generation_historical_and_projected <- 
  full_join(
  korea_electricity_generation, korea_electricity_generation_projected
)

ESMC_and_generation_projected <- inner_join(
  global_ESMC_comprehensive_projected, 
  korea_electricity_generation_historical_and_projected
)

ESPI_gen_projected <- mutate(
  ESMC_and_generation_projected, "ESPI_gen" = 
  coal_electricity_percent*ESMC_coal/100 + 
  oil_electricity_percent*ESMC_oil/100 + gas_electricity_percent*ESMC_gas/100 + 
  nuclear_and_renewables_electricity_percent*0/100
)
```

```{r create_status-quo_projection_dataframe_for_ESPI_gen}

#create status-quo ESPI-gen projection dataframe

korea_electricity_generation_status_quo_projections <- read_csv("https://raw.githubusercontent.com/kp145322/electricity_supply_security/main/korea_electricity_generation_status_quo_projections.csv")

korea_electricity_generation_historical_and_status_quo_projected <- 
  full_join(
  korea_electricity_generation, korea_electricity_generation_status_quo_projections
)

ESMC_and_generation_status_quo_projected <- inner_join(
  global_ESMC_comprehensive_projected, 
  korea_electricity_generation_historical_and_status_quo_projected
)

ESPI_gen_status_quo_projected <- mutate(
  ESMC_and_generation_status_quo_projected, "ESPI_gen" = 
  coal_electricity_percent*ESMC_coal/100 + 
  oil_electricity_percent*ESMC_oil/100 + 
  gas_electricity_percent*ESMC_gas/100 + 
  nuclear_and_renewables_electricity_percent*0/100
)
```

```{r plot_projected_and_historical_ESPI_gen_together}

#create long BPLE ESPIgen projection data

ESPI_gen_projected_long <- ESPI_gen_projected %>%
  add_column(projection = "9th_BPLE")

  # select only required variables to vertically merge BPLE and status quo projections 

ESPI_gen_projected_long_1 <- ESPI_gen_projected_long[c(1,16,17)]

ESPI_gen_projected_long_2 <- subset(ESPI_gen_projected_long_1, year>=2018)

#create long status-quo ESPIgen projection data

ESPI_gen_status_quo_projected_long <- ESPI_gen_status_quo_projected %>%
  add_column(projection = "status_quo")

#cut extraneous data

ESPI_gen_status_quo_projected_long_1 <- 
  ESPI_gen_status_quo_projected_long[c(1,11,12)]

ESPI_gen_status_quo_projected_long_2 <- 
  subset(ESPI_gen_status_quo_projected_long_1, year>=2018)

#create historical long ESPIgen data to plot with projections

ESPI_gen_historical_long <- ESPI_gen[c(1,11)]

ESPI_gen_historical_long_1 <- ESPI_gen_historical_long %>%
  add_column(projection = "historical")

#vertically merge long ESPI_gen projection data for BPLE and status quo

ESPI_gen_projected_comprehensive_long <- rbind(
  ESPI_gen_projected_long_2, ESPI_gen_status_quo_projected_long_2, 
  ESPI_gen_historical_long_1
)

#plot both ESPI_gen projections together

ESPI_gen_projected_comprehensive_long %>%
  ggplot(mapping = aes(x=year, y=ESPI_gen, color=projection)) + 
  ylab(expression(paste("ESP",I[gen]))) + 
  xlab(expression(paste("Year"))) +
  geom_line(method='lm', se=FALSE) + 
  theme_minimal() + 
  expand_limits(y=0) + 
  geom_point(aes(shape=projection)) + 
# geom_vline(xintercept=c(2018), linetype="dotted") +
  labs(title=(expression(paste("Historical and projected ESP", I[gen]))) , 
       subtitle = "South Korea, 1996-2034") + 
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = 
        element_text(hjust = 0.5)) +
  scale_colour_viridis(discrete = T, option = "H" , labels = c("9th BPLE-based projections", "historical values", "status quo-based projections")) +
 # annotate("text", x=2022,y=1100,label="Projected", size=3, text = element_text(family = "A")) + 
 # annotate("text", x=2014,y=1100,label="Historical", size=3, text = element_text(family = "A"))+
  annotate("text", x=2021,y=1750,label="(2022,1824)", size=2.9, text = element_text(family = "A")) +
  annotate("text", x=2028,y=1640,label="(2030,1711)", size=2.9, text = element_text(family = "A")) +
  annotate("text", x=2033,y=1550,label="(2034,1602)", size=2.9, text = element_text(family = "A")) +
  annotate("text", x=2033.5,y=1950,label="(2034,2053)", size=2.9, text = element_text(family = "A")) +
  theme(legend.title = element_blank()) +
  guides(shape=FALSE) +                                      
  theme(text = element_text(family = "A"))
```


# 5. Create table of ESMC results


We produce a table of our calculations of ESMC_coal, ESMC_gas, ESMC_oil, 
historical ESPI_gen, and ESPI_gen projections for 2022, 2030, and 2034 under 
status-quo and BPLE-based assumptions.

Code for APA-style table adapted from Phillip Parker:
[pdparker/apa_style_gt.R](https://gist.github.com/pdparker/1b61b6d36d09cb295bf286a931990159)

```{r create_table_of_ESMC_results}

#create joined dataframe of all historical ESMC and ESPI values as table 1

global_gas_ESMC_5 <- global_gas_ESMC_long_1[c(1,2)]

global_gas_ESMC_6 <- global_gas_ESMC_5 %>%
  rename(ESMC_gas_weighted = "ESMC")

table_1 <- full_join(global_coal_ESMC_1, global_oil_ESMC_1) %>%
  full_join(global_gas_ESMC_6)%>%
  full_join(ESPI_gen_historical_long)

table_1_rounded <- round_half_up(table_1, digits = 0)

table_1_rounded_printed <- table_1_rounded %>%
  gt() %>%
  tab_header(
    title = html("Calculated Historical Values for ESMC<sub>pol-f</sub><sup>1</sup> and ESPI<sub>gen</sub><sup>2"),
    subtitle = "for years 1996-2018 with available data"
  ) %>%
  tab_source_note(md("Original data from the World Bank, U.S. EIA, GIIGNL, and MOTIE<br>
                     1. ESMC<sub>pol-f</sub> represents global values<br>
                     2. ESPI<sub>gen</sub> represents values for South Korea"))%>%
    cols_label(
    year = html("Year"),
    ESMC_coal = html("ESMC<sub>pol-coal"),
    ESMC_oil = html("ESMC<sub>pol-oil"),
    ESMC_gas_weighted = html("ESMC<sub>pol-gas"),
    ESPI_gen = html("ESPI<sub>gen"),
  ) %>%
    opt_table_lines(extent = "default") %>%
    tab_options(
      heading.border.bottom.width = 2,
      heading.border.bottom.color = "black",
      heading.border.bottom.style = "solid",
      table.border.top.color = "black",
      table_body.hlines.color = "black",
      table_body.hlines.style = "solid",
      table_body.hlines.width = 0.5,
      table_body.border.top.color = "black",
      table_body.border.top.style = "solid",
      table_body.border.top.width = 1,
      heading.title.font.size = 11,
      table.font.size = 11,
      heading.subtitle.font.size = 11,
      table_body.border.bottom.color = "black",
      table_body.border.bottom.width = 1,
      table_body.border.bottom.style = "solid",
      column_labels.border.bottom.color = "black",
      column_labels.border.bottom.style = "solid",
      column_labels.border.bottom.width = 1,
      data_row.padding = px(3)
    ) %>%
      opt_table_font(font = "times")

table_1_rounded_printed

# this segment prints table 1 for export
# table_1_rounded_printed %>%
#   gtsave(
#     "tab_1.png", expand = 10,
#   )
```


# 6. Visualize electricity generation proportion by fuel source


```{r create_electricity_generation_area_chart}

korea_electricity_generation_area_chart <- korea_electricity_generation[3:7]

#split Korea generation data into three data frames, make them long data, 
#then combine them vertically and plot with a area chart

korea_electricity_generation_coal_long <- 
  korea_electricity_generation_area_chart[c(1,2)] %>%
  add_column(fuel = "coal") %>%
  rename("percent" = coal_electricity_percent)

korea_electricity_generation_gas_long <- 
  korea_electricity_generation_area_chart[c(1,3)] %>%
  add_column(fuel = "gas") %>%
  rename("percent" = gas_electricity_percent)

korea_electricity_generation_oil_long <- 
  korea_electricity_generation_area_chart[c(1,4)] %>%
  add_column(fuel = "oil") %>%
  rename("percent" = oil_electricity_percent)

korea_electricity_generation_nuclear_and_renewables_long <- 
  korea_electricity_generation_area_chart[c(1,5)] %>%
  add_column(fuel = "nuclear_and_renewables") %>%
  rename("percent" = nuclear_and_renewables_electricity_percent)

#vertically merge the new long data frames 

korea_electricity_generation_area_chart_long <- 
  rbind(korea_electricity_generation_coal_long, 
        korea_electricity_generation_gas_long, 
        korea_electricity_generation_oil_long, 
        korea_electricity_generation_nuclear_and_renewables_long)

#filter for years 1996-2018

korea_electricity_generation_area_chart_long_1 <- 
  filter(korea_electricity_generation_area_chart_long, year>= 1996) %>%
  filter(year <= 2018)

#plot area chart of long generation proportion data frame

korea_electricity_generation_area_chart_long_1 %>% 
  ggplot(mapping=aes(x=year,y=percent,fill=fuel)) + 
     geom_area(alpha=0.6 , size=0.1, colour="black") +
    scale_fill_viridis(discrete = T, option = "H", 
                       
  #begin coerce labels
                       
  labels = c("coal", "gas", "nuclear and renewable", "oil")
  
  #end coerce labels
                       
  ) +
  theme_minimal() +
  labs(title=(expression(paste("Historical electricity generation percent share by fuel"))), 
       subtitle= "South Korea, 1996-2018", 
       caption =
      "Data compiled from BP Statistical Review of World Energy by Our World in Data") +
  ylab(expression(paste("percent share"))) + 
  xlab(expression(paste("Year"))) +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = 
        element_text(hjust = 0.5)) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(family = "A"))
```